\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{a4wide}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{latexsym}
\usepackage[czech]{babel}
\usepackage{graphicx}
\usepackage{pstricks}
\usepackage{verbatim}
\usepackage{amssymb}
\usepackage{colortbl}
\usepackage{tikz}
\usepackage{pgf}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{multirow}

%\usepackage{myshortcuts}

\pgfdeclarelayer{background}
\pgfsetlayers{background,main}

\newtheorem{definition}{Definition}
\newtheorem{theorem}[definition]{Theorem}
\newtheorem{lemma}[definition]{Lemma}
\newtheorem{corollary}[definition]{Corollary}
\newtheorem{proposition}[definition]{Proposition}


\bibliographystyle{plain}

\title{Outlier detection in network traffic}
\date{}


\begin{document}

\noindent Problems:
\begin{enumerate}
\item (probably) There will be a lot of diverging branches, i.e., a lot of threads having different value of a condition.
\item (probably) Bad memory access pattern.
\end{enumerate}

Input: graph $G$; pattern $P=(d_1,d_2, \ldots, d_n)$. $P$ is given as DFS code.


\begin{algorithm}
\caption{\textsc{Prepare-BFS-Kernel}}
\label{alg:compute-support}
\vbox{\textsc{Prepare-BFS-Kernel}(Database graph $G_D$, Number of patterns $N_P$)}
\begin{algorithmic}[1]
\STATE Compute $m_e$, the max number of edges with labels that corresponds to edges in $P$
\STATE Allocate $L_1,\ldots, L_{|P|}, |L_i|=m_e$ for each running kernel.
\STATE Allocate array $F_{ound}$ of $|D|\cdot N_P$ integers and set them to 0.
\RETURN $s$
\end{algorithmic}
\end{algorithm}


\begin{algorithm}
\caption{\textsc{Check-One-Graph}}
\label{alg:compute-support}
\vbox{\textsc{BFS-kernel}(Database graph $G_D$, Pattern $P$)}
\begin{algorithmic}[1]
\FOR{each edge $e$ in $G_D$ that corresponds to $d_1$}
\STATE store the edge in an array $L_1$.
\ENDFOR
\FOR{$\forall i, i\in\{2,\ldots, |P|\}$}
\FOR{each edge $e$ in $G_D$ that corresponds to $d_i$}
%\FOR{$\foreach e'\in L_{i-1}$}
\STATE loop over $L_j, j < i$ and check whether $e$ is a valid extension.
\STATE \textbf{if} $e$ is valid \textbf{then} store the edge in an array $L_i$.
\STATE \textbf{if} there are no valid extensions \textbf{then}  exit.
%\ENDFOR
\ENDFOR
\ENDFOR
\STATE Store $1$ on the position that corresponds to $G_D$ and $P$ in $F_{ound}$.
\RETURN $s$
\end{algorithmic}
\end{algorithm}

\noindent Some observations:
\begin{enumerate}
\item The arrays $L_i$ for each combination of database graph and pattern will be filled differently
  $\Rightarrow$ each thread loops different number of times.
\item Construction of patterns: how big is $N_P$ ? It can be huge, or we have to somehow reduce the
  number of generated patterns. In the worst case there $N_P = N_e\cdot N^{prev level}_P$ patterns,
  where $N_e$ is the number of frequent edges and $N^{prev level}_P$ is the number of patterns on
  previous level. \emph{This is quite a problem}

\item Note to the previous note: it is probably possible to avoid having huge arrays. The patterns
  can be stored in a prefix tree in similar way as the embeddings in our current method.

\item In any case: each kernel is accessing different parts of the memory with stored graph
  $G_D$. The memory locations are disjunct (having no intersections). So each kernel execution
  results in reading the whole database.
\item each kernel reads the whole database at least $|P|$-times !

%\item Note to the previous note: it is probably possible to avoid having huge arrays, but then it is
%  going to be as complex as our current method with more complicated kernel for testing isomorphism.
%  In order to construct an array of all patterns there will be huge amount of device-device
%  transfers: copy the original pattern and add one edge. Or we have to construct a prefix tree in
%  the same way as we are storing the embeddings. 
\item Either way: the number of possible extensions can be potentially quite huge, even if we try
  hard to reduce it. 
\item \textbf{Collection of possible extensions for one pattern means checking isomorphism in one graph and
  find all extensions, which is in fact the same as computing the support of a pattern.}
\end{enumerate}

\noindent Memory: $K$ is the number of concurently executing kernels. $N_P$ is the number of candidate patterns. Then we need $O(m_e\cdot K\cdot |P|)$ memory.


\end{document}


